DATA 605 Week 15

### 2019-05-14 DATA605/MSilva_Assign15.Rmd
More work on assignment 15

Double checking my work
```{r}
lm(Y ~ X)
```

@@

@@

A grocery store sells two brands of a product, the "house" brand and a "name" brand. The manager estimates that if she sells the "house" brand for x dollars and the "name" brand for y dollars, she will be able to sell 81  21x + 17y units of the "house" brand and 40 + 11x  23y units of the "name" brand.

**Step 1.** Find the revenue function R ( x, y ).

@@

@@

>>>>

Double checking my work

```{r}
lm(Y ~ X)
```

@@

First we find the first and second partial derivatives

| First Derivative    | Second Derivative     |
|---------------------|-----------------------|
|$f_x = 24 - 6y^2$    | $f_{xx} = 0$          |
|$f_y = -12xy -24y^2$ | $f_{yy} = -12x - 48y$ |

and $f_{xy} = 12y$.  Now we find the critical points

$$f_x(x,y) = 0 \rightarrow 24 - 6y^2=0 \rightarrow -6y^2 = -24 \rightarrow y^2 = 4 \rightarrow y = \pm 2 $$

$$f_y(x,y) = 0 \rightarrow  -12xy - 24y^2 = 0 \rightarrow-12xy = 24y^2 \rightarrow  x = -2y$$

When y = 2 x = -4 and when y = -2 x = 4.  In order to find the z we plug these values into the function.

```{r}
fxy <- function(x, y){
  24*x-6*x*y^2-8*y^3
}

fxy(4, -2)
fxy(-4, 2)
```

In order to figure out what type of point it is, we need to plug it into the second derivative test.

```{r}
second_derivative_test <- function(x,y){
  #fxx * fyy - fxy^2
  (0 * (-12*x - 48*y))-((12*y)^2)
}

second_derivative_test(4, -2)
second_derivative_test(-4, 2)
```

| Point (x, y, z) | Second Derivative Test | Conclusion   |
|-----------------|------------------------|--------------|
|(4, -2, 64)      | Negative               | Saddle Point |
|(-4, 2, -64)     | Negative               | Saddle Point |

@@

A grocery store sells two brands of a product, the "house" brand and a "name" brand. The manager estimates that if she sells the "house" brand for x dollars and the "name" brand for y dollars, she will be able to sell 81 - 21x + 17y units of the "house" brand and 40 + 11x -23y units of the "name" brand.

**Step 1.** Find the revenue function R (x, y).

$R(x,y) = x(81 - 21x + 17y) + y(40 + 11x - 23y)$

@@

```{r}
revenue <- function(x,y){
  x * (81 - 21 * x + 17 * y) + y * (40 + 11 * x -23 * y)
}

revenue(2.30, 4.10)
```

R(x,y) = $116.62

@@

Let's express the cost equation as a function of x.  Given $x + y = 96$, $y = 96 - x$.

$$C(x)=\frac{1}{6}x^2+\frac{1}{6}(96-x)^2+7x+25(96-x)+700$$

$$C(x)=\frac{x^2}{6}+\frac{1}{6}(96-x)^2-18x+3100$$

$$C(x)=\frac{x^2}{3}-50x+4636$$

Now minimize it

$$C'(x) =  \frac{2x}{3}-50 \rightarrow 0 = \frac{2x}{3}-50 \rightarrow\frac{2x}{3} = 50 \rightarrow 2x = 150 \rightarrow x = 75$$

$$y = 96 - (75) \rightarrow y = 21$$

| Location    | Units |
|-------------|-------|
| Los Angeles | 75    |
| Denver      | 21    |
